### 2019-08-30 reports/thesis/chapters/1_literatureReview.tex
Revise thesis and qq plot for compound poisson
Revise thesis

X-ray computed tomography (XCT) can be used as a non-destructive test for AM products, this is the main theme of this thesis. Various reviews on AM exist such as \cite{kruth1991material, kruth1998progress, pham1998comparison, gibson2010additive, wong2012review, ngo2018additive}. For XCT used in manufacturing, there are \cite{cantatore2011introduction, kruth2011computed, sun2012overview}. \cite{thompson2016x} reviewed the applications of XCT on AM.

@@

Loosely, AM involves solidifying material onto a moving platform so that the object is manufactured layer by layer. Typically this is a slow and expensive method compared to destructive methods such as computer numerical control (CNC) machining for example. However, this is not the full picture. The set up cost for AM is low, in particular destructive methods requires planning and setting up various apparatus before the manufacturing stage \citep{gibson2010additive}. This is why AM used to be called rapid prototyping \citep{kruth1991material}, it was suitable to manufacture bespoke items.

@@

Fused deposition modelling is another liquid based AM technology. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer. In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.000\,1 inches (\SI{0.003}{\milli\metre}).

@@

XCT started its use in the medical field but advancement of the technology saw its use in manufacturing and metrology, the science of measurement. Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}. Reverse engineering is possible when XCT is combined with AM, for example it was used for improving existing hollow engine valves \citep{cooper2015design}. However the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}. This is because there is a lot of inconsistent in the setup of XCT apparatuses and on controlling the sources of error.

@@

The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a bed. An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating through the patient using different paths. X-ray beams were pencil beams in the early versions of XCT \citep{michael2001x}. To reduce scanning times, fan shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}. These multiple x-ray readings can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}. This is illustrated in Figure \ref{fig:literature_medicalct}.

@@

\subsection{Acquisition Process}

High power x-rays can be used in XCT for the purpose of manufacturing and metrology because there is no consequence of the manufactured object absorbing the radiation. The XCT setup is different, the object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically the x-ray is a cone beam \citep{kruth2011computed}. This is illustrated in Figure \ref{fig:literature_xct}.

@@

The efficiency of an x-ray tube is poor, 99\% of the energy from electrons is converted to heat, the rest to x-rays \citep{kruth2011computed}.

Photons, making up the radiation, are emitted from the x-ray tube as a Poisson process \citep{cierniak2011x}. The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode. The energy of each photon are from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies \citep{sun2012overview}. An example is shown in Figure \ref{fig:literature_spectrum}.

@@

The scanned object are exposed to x-ray photons which undergoes attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}. The object can absorb the photons via the photoelectric effect. In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the object's atom \citep{millikan1916direct}. Photons can be scattered by the object by colliding inelastically with and transfers its energy to an electron. This process is known as Compton scattering \citep{compton1923quantum}. The photoelectric effect and Compton scattering make a number of photons undetectable. However if some of the photons avoid these processes, they are detected and their energy is left unaffected.

Beer's law simplifies these quantum mechanistic process. Suppose the x-ray beam with rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis. Let $\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has rate of emission $I$ after attenuation. A differential equation can be set up to model the decay of photons as it attenuate through the object such that
\begin{equation}
\dfrac{\diff I}{\diff x} = -I\mu(x)
\end{equation}
which can be solved
\begin{equation}
I = I_0\exp\left[\int_{x \in \text{path of photon}}-\mu(u)\diff u\right] \ .
\label{eq:beerLaw}
\end{equation}
However, the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}. Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law. In general low energy photons are more likely to be absorbed and scattered than high energy photons, this increases the average energy of the detected photons \citep{sun2012overview}. This is called beam hardening.

@@

Not all of the visible light pulses are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x, ren2018tutorial}. The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.

@@

There exist many reconstruction algorithms in XCT \citep{smith1990cone} such as the filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}. Once the reconstruction has been done, the shape or surface can be extracted by use of thresholding \citep{kruth2011computed}. There exist many software for the reconstruction stage of XCT \citep{reinhart2008industrial, sun2012overview}.

@@

XCT can be used to measure the length of the object, making it useful for measuring AM objects internally and externally. \emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD model \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.

@@

The set up of XCT has a number of variables. The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray projection. The exposure time is also a factor. These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}. The magnification can be adjusted by adjusting the distances between the x-ray tube, the object and the x-ray detector. Increasing the magnification increases the image resolution but can cause blurry images, this is the result from using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}. Larger spot sizes cause more blurry results, this is known as the penumbra effect \citep{kueh2016modelling}. However, spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube.

@@

There is also the question on how to orient the object on the turntable \citep{corcoran2016observations} as well as how many angles to use \citep{kruth2011computed}. More angles produce a more accurate reconstruction but requires more acquisition time. Figure \ref{fig:literature_angles} shows an example of a reconstruction using various number of angles.

@@

Problems can occur in the detector. For examples pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}. Spatially correlated noise within a projection can be observed \citep{sun2016characterisation} as well as correlation between acquisitions, this is known as image lag \citep{yang2009evaluation}. Precautions can be taken reduce the impact from image lag such as waiting for 20 minutes between acquisitions \citep{yang2010noise}.

Errors due to beam hardening can occur. Low energy photons are more likely to be absorbed or scattered, this causes a few millimetres of the surface of the object to absorb or scatter more photons than the interior. This can cause flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed} as well as artefacts \citep{sun2016applications}. Beam hardening can be tackled by eliminating the low energy photons by placing a thin metal plate, called a filter, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper. Figure \ref{fig:literature_hardening} shows an example of a reconstruction with and without a filter, without the filter the outer perimeter appears less dense than it should be.  A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}. Early reconstruction algorithms assumed no beam hardening but it can be corrected using modern methods \citep{elbakri2001statistical, sun2016applications}.

@@

The most common reconstruction method is the FDK \citep{feldkamp1984practical} algorithm as it caters for cone beams. However it assumes a circular trajectory from the source which can cause artefacts if assumptions are not met \citep{sun2016applications}.

@@

The most common use of XCT in AM is the investigation of pores in the manufactured object \citep{thompson2016x}. Pores can be classified as defects if the pores are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}. The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}. Accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.

An advantage of XCT is that the location of the pores can be visualised, for example in Figure \ref{fig:literature_pores3D}, and compared to the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}. Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}. The location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}. In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD model and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}, an example is shown in Figure \ref{fig:literature_warnett}.

@@

One of the disadvantages of XCT is that it is a slow process. XCT is not an instantaneous process so progress bars are usually featured in XCT marketing such as \cite{nikon2015inline}'s inline quality control. The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards} however more images would improve the accuracy of the reconstruction \citep{kruth2011computed}. \cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction. This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}. Fewer angular projections were taken but they can be obtained in one go, speeding up the process.

@@

Instead of reconstructing the object, the analysis can be done on the projections itself, or in projection space, by comparing it to a simulated projection produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \cite{brierley2018optimized} developed an algorithm to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition. It is however very complicated as it is optimising over a very large dimensional space. \cite{brierley2018optimized} also demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without. Another method is to use machine learning methods to classify defects from a projection \citep{rale2009comparison}.

It is however inevitable that accuracy is lost from the jump from reconstruction space to projection space, for example, a CT scan has superior performance in the diagnostic of pneumonia compared to a chest radiograph \citep{hayden2009chest}.

>>>>

X-ray computed tomography (XCT) can be used as a non-destructive test for AM products. Various reviews on AM exist such as \cite{kruth1991material, kruth1998progress, pham1998comparison, gibson2010additive, wong2012review, ngo2018additive}. For XCT used in manufacturing, there are \cite{cantatore2011introduction, kruth2011computed, sun2012overview}. \cite{thompson2016x} reviewed the applications of XCT on AM.

@@

Loosely, AM involves solidifying material onto a moving platform so that the object is manufactured layer by layer. Typically this is a slow and expensive method compared to destructive methods such as computer numerical control (CNC) machining for example. An advantage of AM is that the set up cost is low, in particular, destructive methods requires planning and setting up various apparatus before the manufacturing stage \citep{gibson2010additive}. This makes it suitable to manufacture bespoke items which achieves the goals of AM's predecessor called rapid prototyping \citep{kruth1991material}.

@@

Fused deposition modelling is another liquid based AM technology. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $xy$ plane, or left to right and front to back, to produce a layer. The jetting head can move in the $z$-axis, or up and down, to manufacture the next layer. In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.000\,1 inches (\SI{0.003}{\milli\metre}).

@@

XCT started its use in the medical field but advancement of the technology saw its use in manufacturing and metrology, the science of measurement. Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}. XCT can be used to reverse engineer existing products and improved. The improved can be fabricated using AM, for example, it was used for improving existing hollow engine valves \citep{cooper2015design}. However the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}. This is because there is a lot of inconsistencies in the setup of XCT apparatuses and on controlling the sources of error.

@@

The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a flat bed. An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating through the patient using different paths. X-ray beams were pencil beams in the early versions of XCT \citep{michael2001x}. To reduce scanning times, fan shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}. These multiple x-ray readings can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}. This is illustrated in Figure \ref{fig:literature_medicalct}.

@@

\subsection{Acquisition Process in Manufacturing}

In manufacturing and metrology, high power x-rays can be used in XCT because there is no consequence of the manufactured object absorbing the radiation. The XCT setup is different, the object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically the x-ray is a cone beam \citep{kruth2011computed}. This is illustrated in Figure \ref{fig:literature_xct}.

@@

The efficiency of an x-ray tube is poor. 99\% of the energy from electrons is converted to heat, the rest to x-rays \citep{kruth2011computed}.

Photons, making up the radiation, are emitted from the x-ray tube which can be modelled as a Poisson process \citep{whiting2006properties, cierniak2011x}. The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode. Sources of energy of each photon come from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies \citep{sun2012overview}. An example is shown in Figure \ref{fig:literature_spectrum}.

@@

The scanned object is exposed to x-ray photons which undergo attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}. The object can absorb the photons via the photoelectric effect. In the photoelectric effect, the photons transfer all its energy to a bounded electron and ejects it from the object's atom \citep{millikan1916direct}. Photons can be scattered by the object by colliding inelastically with and transfers its energy to an electron. This process is known as Compton scattering \citep{compton1923quantum}. The photoelectric effect and Compton scattering make a number of photons undetectable. However if some of the photons avoid these processes, they are detected and their energy is left unaffected.

Beer's law simplifies these quantum mechanistic process. Suppose the x-ray beam with rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis. Let $\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has rate of emission $I$ after attenuation. A differential equation can be set up to model the decay of photons as it attenuate through the object such that
\begin{equation}
\dfrac{\diff I}{\diff x} = -I\mu(x)
\end{equation}
which can be solved
\begin{equation}
I = I_0\exp\left[\int_{x \in \text{path of photon}}-\mu(u)\diff u\right] \ .
\label{eq:beerLaw}
\end{equation}
However, the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}. Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law. In general low energy photons are more likely to be absorbed and scattered than high energy photons, which increases the average energy of the detected photons \citep{sun2012overview}. This is called beam hardening.

@@

Not all of the visible light pulses are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x, ren2018tutorial}. This makes the detection a two stage process, converting the x-ray photons into visible light which are then detected \citep{cierniak2011x}. There exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct} but this is unrivalled by solid state CT systems, such as sintillator-photodiodes detectors, which have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.

@@

A number of reconstruction algorithms in XCT have been developed \citep{smith1990cone} such as the filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}. Once the reconstruction has been done, the shape or surface can be extracted by use of thresholding \citep{kruth2011computed}. There are many software packages available for the reconstruction stage of XCT \citep{reinhart2008industrial, sun2012overview}.

@@

XCT can be used to measuring lengths and distances, making it useful for measuring the dimensions of AM objects internally and externally. \emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD model \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.

@@

The set up of XCT has a number of variables. The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray projection. The exposure time is also a factor. These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}. The magnification can be modified by altering the distances between the x-ray tube, the object and the x-ray detector. Increasing the magnification increases the image resolution but can cause blurry images, this is the result from using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}. Larger spot sizes cause more blurry results, this is known as the penumbra effect \citep{kueh2016modelling}. However, spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube.

@@

There is also the question on how to orient the object on the turntable \citep{corcoran2016observations} as well as how many angles to use \citep{kruth2011computed}. More angles produce a more accurate reconstruction but requires more acquisition time. Figure \ref{fig:literature_angles} shows an example of a reconstruction using various numbers of angles.

@@

Problems can occur in the detector. For example, pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}. Another problem is that there exist spatially correlated noise within a projection which can detected experimentally \citep{sun2016characterisation} as well as correlation between acquisitions, known as image lag \citep{yang2009evaluation}. Precautions can be taken reduce the impact from image lag such as waiting for 20 minutes between acquisitions \citep{yang2010noise}.

Errors due to beam hardening can occur. Low energy photons are more likely to be absorbed or scattered, which causes a few millimetres of the surface of the object to absorb or scatter more photons than the interior. This can cause artefacts \citep{sun2016applications} such as flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed}. Beam hardening can be tackled by eliminating the low energy photons by placing a filter, a thin metal plate, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper. Figure \ref{fig:literature_hardening} shows an example of a reconstruction with and without a filter, without the filter the outer perimeter appears less dense than it should be.  A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}. Early reconstruction algorithms ignored beam hardening but modern methods can take beam hardening into account \citep{elbakri2001statistical, sun2016applications}.

@@

The most common reconstruction method is the FDK \citep{feldkamp1984practical} algorithm because it caters for cone beams. However, it assumes a circular trajectory from the source which can cause artefacts if the trajectory is actually not circular \citep{sun2016applications}.

@@

The most common use of XCT in AM is the investigation of pores in the manufactured object \citep{thompson2016x}. Pores can be classified as defects if the pores are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}.

The porosity is defined by dividing the volume of all of the pores by the volume of solid material \citep{taud2005porosity}. This can be used to quantified the material's strength and can be measured accurately using Archimedes' method \citep{spierings2011comparison}. Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage} and it was found the location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}. XCT can be used to measure porosity and has an advantage over Archimedes' method because the location of the pores can be visualised in XCT. An example of visualising pores is shown in Figure \ref{fig:literature_pores3D} and the pores can be compared to the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}. In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD model and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}, an example is shown in Figure \ref{fig:literature_warnett}.

@@

One of the disadvantages of XCT is that it is a slow process. XCT is not an instantaneous process so progress bars are usually featured in XCT marketing such as \cite{nikon2015inline}'s inline quality control. The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards}. More angular projections would take more time but will improve the accuracy of the reconstruction \citep{kruth2011computed}. \cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction. This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}. Fewer angular projections were taken but they can be obtained in one go, speeding up the process.

@@

Instead of reconstructing the object, the analysis can be done on the projections itself, or in projection space, by comparing it to a simulated projection produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. It can simulate projections of the object given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the CAD of the object \citep{bellon2011simulation, deresch2012simulating}.

An algorithm was developed to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition \citep{brierley2018optimized}. However, it is very complicated as it is optimising over a very large dimensional space \citep{brierley2018optimized}. It was demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without \citep{brierley2018optimized}. Another method is to use machine learning methods to classify defects from a projection \citep{rale2009comparison}.

It is however inevitable that accuracy is lost from the transition from reconstruction space to projection space, for example, in the diagnostic of pneumonia, a CT scan has superior performance compared to a chest radiograph \citep{hayden2009chest}.
